Visualization

### 2020-09-07 analysis/visualization.Rmd

fd_table %>%
  filter(metric == "FRic") %>%
  left_join(metadata %>% select(study_id, climate)) %>%
  unite(id, study_id, plot) %>%
  ggplot(aes(x = year, y = log(value))) +
  geom_smooth(aes(color = climate, group = id), method = "glm", se = FALSE) +
  geom_point(aes(color = climate, group = id)) +
  geom_smooth(color = "black", method = "glm", se = FALSE) +
  theme(legend.position = "none") 
```

>>>>

fric_trend <- fd_table %>%
  filter(metric == "FRic") %>%
  left_join(metadata %>% select(study_id, climate)) %>%
  ggplot(aes(x = year, y = log(value))) +
  # geom_smooth(aes(color = climate, group = plot_id), method = "glm", se = FALSE) +
  # geom_point(aes(color = climate, group = plot_id)) +
  geom_smooth(aes(group = plot_id), color = "grey", method = "glm", se = FALSE) +
  geom_point(aes(group = plot_id) ,color = "grey") +
  geom_smooth(color = "black", method = "glm", se = FALSE) +
  theme(legend.position = "none") 
ggsave("fric_trends.png", fric_plot)
```

metric plotting function
```{r}
library(lme4)

plot_metric <- function(metric_name, ylabel){
  data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logvalue = log(value))

  mod <- lmer(logvalue ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

  print(metric_name) 
  print(summary(mod))
  confint(mod)

  pred <- data.frame(year = min(data$year):max(data$year)) %>%
    mutate(pred = coefs[1,1] + year * coefs[2,1])

  trend_plot <- data %>%
    left_join(pred, by = "year") %>%
    #left_join(metadata %>% select(study_id, climate)) %>%
    ggplot(aes(x = year, y = logvalue)) +
    # geom_smooth(aes(color = climate, group = plot_id), method = "glm", se = FALSE) +
    # geom_point(aes(color = climate, group = plot_id)) +
    geom_point(aes(group = plot_id) ,color = "grey") +
    geom_smooth(aes(group = plot_id), color = "darkgrey", method = "glm", se = FALSE) +
    #geom_smooth(color = "black", method = "glm", se = FALSE) +
    geom_line(mapping = aes(y = pred)) +
    theme(legend.position = "none") +
    theme_classic() +
    ylab(ylabel)

  ggsave(paste0(metric_name, "_trend.png"), trend_plot)
  return(trend_plot)
}

plot_metric("FRic", "log(FD)")

plot_map <- tibble(metric_name = c("FRic", "FEve", "FDiv", "FDis"), 
           ylabel = c("log(FD)", "log(Evenness)", "log(Divergence)", "log(Dispersion)"))
pmap(plot_map, plot_metric)
```

get model info
```{r}
get_metric_conint <- function(metric_name){
 data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logvalue = log(value))

  mod <- lmer(logvalue ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

  confint(mod)
  # as_tibble(confint(mod)) %>%
  #   mutate(metric = metric_name)
}

map(c("FRic", "FEve", "FDiv", "FDis"), get_metric_conint)
```
